Tobacco

### 2023-07-13 docsrc/documentation/notebooks/tobacco.Rmd
Started a notebook for physical activity documentation

---
title: "Tobacco"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

## Tobacco

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

@@

```{r tobacco_data}
counts_density('ncigs')
```

@@

age. persons age. generally older people and very young smoke. 
SF_12. wellbeing estimates number of cigarettes smoked.
labour_state. whether a person is employed or not.
ethnicity. certain ethnicities more likely to smoke cigarettes. 
education_state. highest qualification.
job_sec job quality
hh_income household income
ncigs previous number consumed.

@@

ethnicity. certain ethnicities more likely to smoke cigarettes. 
labour_state. whether a person is employed or not.
age
SF_12. wellbeing estimates number of cigarettes smoked.
ncigs previous number consumed.

@@

Almost all coefficients significant. Particularly prevous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes.

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
```

>>>>

---
title: "Tobacco"
output:
  pdf_document: default
  html_document: default
bibliography: docsrc/refs.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```
## Tobacco

@@

```{r load_data, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```

@@

```{r tobacco_data}
counts_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", "y")
```

@@

- age. persons age. generally older people and very young smoke. 
- SF_12. wellbeing estimates number of cigarettes smoked.
- labour_state. whether a person is employed or not.
- ethnicity. certain ethnicities more likely to smoke cigarettes. 
- education_state. highest qualification.
- job_sec job quality
- hh_income household income
- ncigs previous number consumed.

@@

- ethnicity. certain ethnicities more likely to smoke cigarettes. 
- labour_state. whether a person is employed or not.
- age
- SF_12. wellbeing estimates number of cigarettes smoked.
- ncigs previous number consumed.

@@

Almost all coefficients significant. Particularly previous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes.

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("data/transitions/ncigs/zip/ncigs_2018_2019.rds")
zip_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", 'y')
```
